Exploring Income Inequality in US after financial crises: Analysis

### 2024-04-14 paper/paper.qmd
Update paper.qmd

---
title: "Exploring Income Inequality in US after financial crises: Analysis"
subtitle: "Insights from 2002 to 2019"
author: "Dong Jun Yoon"
thanks: "Code and data are available at: https://github.com/DJY1231/Exploring-Income-Inequality-in-US.git"
date: today
date-format: long
abstract: "This paper investigates income inequality in United States from 2002 to 2019 using data from various surveys. Through exploratory data analysis and regression modeling, we uncover increasing income inequality trends over time and variations across different provinces. Our findings reveal nuanced relationships between temporal trends and regional disparities, and income distribution dynamics. Through rigorous analysis, we uncover two key findings: a consistent rise in income inequality over time, significant regional disparities across provinces. Understanding these dynamics is important for policymakers to develop targeted strategies aimed at mitigating income inequality and promoting social and economic equity in United States."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

>>>>

---
title: "Exploring Income Inequality in US after financial crises: Analysis"
subtitle: "Insights from 2002 to 2019"
author: "Dong Jun Yoon"
thanks: "Code and data are available at: https://github.com/DJY1231/Exploring-Income-Inequality-in-US.git"
date: today
date-format: long
abstract: "This paper investigates income inequality in the United States from 2002 to 2019 using data from the United States Census and the World Inequality Database (WID). Throughout the paper, we will explore trends in income inequality, examining whether it is increasing or decreasing over time, and how the Great Recession of 2007-2009 affected income inequality. We will utilize data analysis and regression modeling to investigate these trends. Investigating these trends is significant, as it could assist policymakers or the government in developing strategies that could decrease the inequalities occurring within the country. As a result, this report may be used to help promote social and economic equity in the United States."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Data - wid - world inequality database. WID. (n.d.). https://wid.world/data/
